Methods for Large Scale Learning to Rank

### 2014-04-07 report/Chapters/CrossBenchmarkComparison.tex
nieuwe export graphic
raw data in appendix

\subsection{All metrics}
\begin{figure}[!h]
\includegraphics[scale=0.40]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?
%TODO: limitations van deze vergelijkingsmethodologie

>>>>

\subsection{All metrics}
Figure \ref{fig:normalised_winning_number_all} shows the normalised winning number as function of ideal winning number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum} and Table \ref{tab:raw_data_norm_winnum_cntd} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?
%TODO: limitations van deze vergelijkingsmethodologie
